%!TEX root = project.tex

\chapter*{About this project}
\paragraph{Abstract}
Social media today plays an expanding significant role in society, the information technology industry and the field of computer science. The use of social media is a hot-topic for many organizations, with the aim to identify approaches in which companies can use applications to increase profits and grow product awareness. On a day-to-day basis, users from across the globe are becoming increasingly frustrated, wasting valuable time, scrolling through irrelevant content while companies are wasting money advertising to users outside their market.  In order to achieve the optimal benefits from social media, for both users and businesses, the development of these technologies require approaches that focus on specific human interests and values.

\paragraph{}
This project aims to deliver a solution by developing a platform with the goal of delivering a social experience that targets a specific user base. As the authors are in the field of computer science the focus of the content will be to appeal to the tech savvy user. The proposed solution will be a web application that will offer a unique online community to users and businesses interested in technology. 

\paragraph{Authors}
This project was developed as a 15 credit project by Kevin Barry and Cian Gannon, final year students of Software Development at Galway Mayo Institute of Technology.

\paragraph{Acknowledgements}
The authors of this project would like to acknowledge and thank the project supervisors Martin Keniron and Dr. John Healy of GMIT for offering their time and advice throughout this project.
\input{sections/introduction.tex}
\input{sections/context.tex}
\input{sections/methodology.tex}
\input{sections/technology.tex}
\input{sections/systemdesign.tex}
\input{sections/evaluation.tex}
\input{sections/conclusion.tex}
\input{sections/appendices.tex}







