\chapter{System Evaluation}
Reﬂecting on the objectives discussed in \textit{1.1: ProjectObjectives} ,the following is a condensed initial list of objectives for both the dissertation and applied aspects this project: 

\begin{itemize}
\item [\textbf{Dissertation}]
\item Introduce the concept of the project. 
\item Provide an understanding of social media.
\item Provide a understanding of web technologies.
\item Describe the development of the applied project
\end{itemize}
 
\begin{itemize}
\item [\textbf{Applied Project}]
\item Produce a simple easy to use web application.
\item Deliver a social platform for tech savy people that differs from the norm.
\item Dive into new web technologies.
\item Complete the project collaborating as a team using an efficient and effective approach.
\end{itemize}



% ========================== Testing ========================== 
\section{Testing}
is it robust?
what type of testing?
 Prove that your software is robust. How? Testing etc. 
\subsection{Unit Testing}
testing parts of program
\subsection{Beta Testing}
giving the program to peers

% ========================== Performance ========================== 
\section{Performance}
Use performance benchmarks (space and time) if algorithmic.

% ========================== Objectives ========================== 
\section{Evaluation of Objectives}
Measure the outcomes / outputs of your system / software against the objectives from the Introduction.
\subsection{Objective 1}
did we reach our objective?

\subsection{Objective 2}
did we reach our objective?

\subsection{Objective 3}
did we reach our objective?

\subsection{Objective 4}
did we reach our objective?

% ========================== Limitations ========================== 
\section{Limitations}
Areas for improvement?
Highlight any limitations or opportuni-ties in your approach or technologies used.